Formal Synthesis of Digital Controllers for Observable Continuous Plants with Transient Performance Specifications

### 2018-01-25 TACAS2018/paper.tex
more editing of the synthesis sec

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
%\subsection{Using optimization refinement for CEGIS of control systems}\label{sec:cof_synth}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
In this section, we describe our technique for synthesizing safe
digital feedback controllers using CEGIS. Broadly speaking, CEGIS
denotes an iterative technique where each iteration performs inductive
generalisation based on counterexamples provided by a verification
engine.
%
We build upon this paradigm to create CEGIS-OR (CEGIS with Optimization
and Refinement).
Our approach is illustrated in Figure~\ref{fig:CEGIS-OR} and consists of four main
phases:
\begin{itemize}
\item {\sc Abstract}: constructs an unsound abstract model that over-approximates
the dynamics of the system.
\note{what does it mean to be over-approximating but unsound?}
\item {\sc synthesize}: generates a candidate controller and observer.
  As it makes use of the potentially coarse abstraction constructed by {\sc Abstract},
  the candidate doesn't necessarily meet the stability or safety specification.
  %% these do not necessarily meet any portion
  %% of the specification, but either through optimization or refinement become
  %% more precise (therefore more likely to meet the specification) with each iteration.
\item {\sc model}: refines the abstraction needed by {\sc Abstract}
  in order to reduce the probability of failure in the next iteration.
  \note{{\sc abstract} doesn't need an abstraction.}
  \note{how about optimization?}
\item {\sc verify}: verifies the behaviour of the candidate controller and observer
  against a sound over-approximation of the concrete dynamics of the system for an infinite space over an infinite time horizon. If the verification fails, produces a counterexample
  describing the reason for failure.
\end{itemize}

\note{this needs to be integrated in the above enumeration}
Our optimization procedure aims at reducing the
size of the reach space of the closed loop system while maintaining other
verification properties. \note{what are other verification properties?
if you mean safety and stability say so.}
%% The first one aims at making the system as
%% convergent as possible.  This does not only ensure stability, but reduces
%% the response time of the system, moving away from the unsafe states faster.
%% The second one seeks to minimize rotations.  If the system rotates slower, it
%% is less likely to reach unsafe states before converging.
%% In both cases, the shape of the eigenspace may affect us negativey, so we
%% use a measure of the size of the reach space to guide our optimization.

@@

The main advantage of this approach is two-fold:
\begin{itemize}
\item[1.] We start with simpler (i.e. imprecise) abstractions that get
  refined into more complex ones as the procedure progresses. Thus, solutions
  that don't require a high level of precision are obtained fast. 
\item[2.] Although {\sc synthesize} makes use of a potentially coarse abstraction,
  by optimizing the candidate solution in each iteration of the CEGIS loop
  we obtain better candidates that are more likely to meet the
  specification or produce high quality counterexamples in the
  {\sc verify} phase.
  This has the potential to reduce
  the number of iterations of the CEGIS loop required to obtain a solution.
\end{itemize}

>>>>

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
%\subsection{Using optimization refinement for CEGIS of control systems}\label{sec:cof_synth}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

In this section, we describe our technique for synthesizing safe
digital feedback controllers using CEGIS. Broadly speaking, CEGIS
denotes an iterative technique where each iteration performs inductive
generalisation based on counterexamples provided by a verification
engine. In each iteration, an inductive synthesiser produces a
candidate solution that obeys the specification for a limited number
of inputs. Subsequently, this candidate is passed to a verification
oracle that checks it against the specification for all possible
inputs. If the verification fails, then the witness counterexample is
passed back to the synthesis phase, where it is added to the set of
inputs to be considered in the next loop iteration. Otherwise, we are
done.

%
We enhance the standard CEGIS architecture with abstraction refinement
and optimization, resulting in CEGIS-OR (CEGIS with Optimization and
Refinement).  By using abstraction refinement, CEGIS-OR tackles the
scalability issues inherent in program synthesis as it allows using
potentially coarse abstractions of a system that are only refined on
demand.  Given that the use of coarse abstractions could result in low
quality candidate solutions (i.e. candidates that fail the
specification on a very large number of inputs), after each synthesis
phase we use optimization techniques to improve the produced
candidates.  In particular, our optimization procedure aims at
reducing the size of the reach space of the closed loop system while
maintaining other verification properties. \note{what are other
  verification properties?  if you mean safety and stability say so.}

Our approach is illustrated in Figure~\ref{fig:CEGIS-OR} and consists of four main
phases:
\begin{itemize}
\item {\sc Abstract}: constructs an unsound abstract model that over-approximates
the dynamics of the system.
\note{what does it mean to be over-approximating but unsound?}
\item {\sc synthesize}: generates a candidate controller and observer.
  As it makes use of the potentially coarse abstraction constructed by {\sc Abstract},
  the candidate doesn't necessarily meet the stability or safety specification.
  %% these do not necessarily meet any portion
  %% of the specification, but either through optimization or refinement become
  %% more precise (therefore more likely to meet the specification) with each iteration.
\item {\sc model}: refines the abstraction needed by {\sc Abstract}
  in order to reduce the probability of failure in the next iteration.
  \note{{\sc abstract} doesn't need an abstraction.}
  \note{how about optimization?}
\item {\sc verify}: verifies the behaviour of the candidate controller and observer
  against a sound over-approximation of the concrete dynamics of the system for an infinite space over an infinite time horizon. If the verification fails, produces a counterexample
  describing the reason for failure.
\end{itemize}

%% The first one aims at making the system as
%% convergent as possible.  This does not only ensure stability, but reduces
%% the response time of the system, moving away from the unsafe states faster.
%% The second one seeks to minimize rotations.  If the system rotates slower, it
%% is less likely to reach unsafe states before converging.
%% In both cases, the shape of the eigenspace may affect us negativey, so we
%% use a measure of the size of the reach space to guide our optimization.

@@

The main advantage of this approach is two-fold:
\begin{itemize}
\item[1.] We start with coarse abstractions that get
  refined into more complex ones as the procedure progresses. Thus, solutions
  that don't require a high level of precision are obtained fast. 
\item[2.] Although {\sc synthesize} makes use of a potentially coarse abstraction,
  by optimizing the candidate solution in each iteration of the CEGIS loop
  we obtain better candidates that are more likely to meet the
  specification or produce high quality counterexamples in the
  {\sc verify} phase.
  This has the potential to reduce
  the number of iterations of the CEGIS loop required to obtain a solution.
\end{itemize}
